Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 113

We also coded the extent to which data and code was specific to software that was not freely available. When open source software is used, the analyses can be reproduced by anyone with a computer and internet, regardless of whether they have bought the same software package. When proprietary software is used, results might still be reproducible by anyone, but it could require more effort to do so. For example, SPSS produces proprietary .sav and .sps files. However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded into R. Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available. The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files required dedicated EEG software and could not be reproduced (we could also not find the analysis code for this article).

>>>>

We also coded the extent to which data and code were specific to software that was not freely available. When open source software is used, the analyses can be reproduced by anyone with time, a computer and internet. When proprietary software is used, results might still be reproducible in principle, but could require more effort to do so. For example, SPSS produces proprietary .sav and .sps files. However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded in R. Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available. The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files required dedicated EEG software and could not be reproduced (we could also not find the analysis code for this article).
